Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-10 bbbq_article.tex

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2a.png}
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs for the proteomes of human
    that is predicted 
    (outer bars, same as figure 1A for human only) 
    and is observed to occur naturally (inner bars/lines)
    (from elution studies)
    per MHC allele
  }
  \label{fig:elution}
\end{figure}

>>>>

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2a.png}
    \label{fig:2a}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2b.png}
    \label{fig:2b}
  \end{subfigure}

  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2c.png}
    \label{fig:2c}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
    \label{fig:2d}
  \end{subfigure}  
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    (A) x
    (B) x
    (C) IEDB MHC ligands
    (D) IEDB T cells
  }
  \label{fig:elution}
\end{figure}
